\documentclass[11pt, a4paper]{article}
\usepackage[inner=1.5cm,outer=1.5cm,top=2.5cm,bottom=2.5cm]{geometry}
\pagestyle{empty}
\usepackage{graphicx}
\usepackage{fancyhdr, lastpage, bbding, pmboxdraw}
\usepackage{fancyvrb}
\usepackage[usenames,dvipsnames]{color}
\definecolor{blue}{rgb}{0,0,.6}
\usepackage[colorlinks,pagebackref,pdfusetitle,urlcolor=blue,citecolor=blue,linkcolor=blue,bookmarksnumbered,plainpages=false]{hyperref}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\pagestyle{fancyplain}
\fancyhf{}
\lhead{ \fancyplain{}{AP Calculus AB} }
\rhead{ \fancyplain{}{\today} }
\fancyfoot[RO, LE] {page \thepage\ of \pageref{LastPage} }
\thispagestyle{plain}

\begin{document}
\begin{center}
{\Large \textsc{Syllabus: AP Calculus}}
\end{center}
\begin{center}
Fall 2019
\end{center}


\begin{center}
\rule{6in}{0.4pt}
\begin{minipage}[t]{.75\textwidth}
\begin{tabular}{llcccll}
\textbf{Instructor:} & Connor Hargus & & &  & \textbf{Time:} & TBD \\
\textbf{Email:} &  \href{mailto:connorhargus@gmail.com}{connorhargus@gmail.com} & & & & \textbf{Place:} & TBD
\end{tabular}
\end{minipage}
\rule{6in}{0.4pt}
\end{center}
\vspace{.5cm}
\setlength{\unitlength}{1in}
\renewcommand{\arraystretch}{2}

\noindent\textbf{Objectives:}  This course is designed to give students the core intuitions behind differential calculus, integral calculus, and limits, as well as give an understanding of the incredible usefulness of calculus in the real world. In the process, we will cover all the required material for the AP Calculus AB test.

\vskip.15in
\noindent\textbf{Prerequisites:}
Pre-calculus (arithmetic, geometry, algebra, trigonometry, linear functions, etc.)

\vspace*{.15in}
\noindent\textbf{Grading Policy:} Homework (40\%),  Attendance (20\%), Quizzes (10\%),  Tests (30\%). 

\vskip.15in
\noindent\textbf{Class Guidelines:}  
\begin{itemize}
\item Bring A4-size paper to class every day.
\item Never be afraid to ask questions at any time during class. If you do not understand something, whether about Calculus or the English terms I use, let me know immediately so that I can help you.
\item Do not disrupt other students' learning. 
\end{itemize}

\vskip.15in
\noindent\textbf{Attendance:}  
\begin{itemize}
\item Calculus is a class which builds up knowledge over time in a specific order. If you do not come to class, it will be hard for you to catch up. Therefore, regular and on time attendance is essential and expected. Let me know if there is an emergency circumstance preventing you from coming to class so that we can work out a plan.
\end{itemize}
\begin{itemize}
\item I will deduct 3\% from your attendance grade each time you are late, and 10\% each time you are absent without an excuse.
\item In order to be given full points in attendance, you must also participate in class.
\end{itemize}

\vskip.15in
\noindent\textbf{Homework:}  
\begin{itemize}
\item Homework will be handed out in class, and will usually be due the following day. Note: Homework will be collected at the \textbf{beginning} of class on the assigned due date.
\item You must show your work, starting from the problem statement and working through to the solution. You may work on homework in groups, but each person must write their own solutions.
\item \textbf{Late policy}: For homeworks, I will deduct 10\% from your score for each late day up to 5 days after the due date. For example, if you do not submit at the beginning of class on the due date you have until the end of class the next to submit with a penalty of 1 late day or 10\%.
\end{itemize}

\vskip.15in
\noindent\textbf{Academic Honesty:}   Copying others' work, whether on homework or tests, is strictly prohibited and will result in both a score of zero and further punitive measures according to the severity of the infraction. Lack of knowledge of this policy is not a reasonable explanation for a violation, as I will go over this policy in class.

\end{document} 